### 2025-06-10 intro.qmd
20250308 - update citations
20250609 - copyediting

This book was originally written for a undergraduate-level course entitled, "Fantasy Football: Predictive Analytics and Empiricism".
The chapters provide an overview of topics that each could have its own class and textbook, such as [causal inference](causal-inference.qmd), [factor analysis](factor-analysis.qmd), [cluster analysis](cluster-analysis.qmd), [principal component analysis](pca.qmd), [machine learning](machine-learning.qmd), [cognitive biases](cognitive-bias.qmd), [modern portfolio theory](modern-portfolio-theory.qmd), [data visualization](data-visualization.qmd), [simulation](simulation.qmd), etc.
The book gives readers an overview of the breadth of the approaches to prediction and empiricism.
As a consequence, the book does not cover any one technique or approach in great depth.

@@

Skills in statistics, statistical programming, and data analysis are highly valuable.
This book includes practical and conceptual tools that build a foundation for critical thinking.
The book aims to help readers evaluate theory in the light of evidence (and vice versa) and to refine decision making in the context of uncertainty.
Readers will learn about the ways that psychological science (and related disciplines) poses questions, formulates hypotheses, designs studies to test those questions, and interprets the findings, collectively with the aim to answer questions, improve decision making, and solve problems.

@@

Here is a video of a Professor Benjamin Motz that describes the value of teaching statistics through the lens of fantasy football:

>>>>

This book was originally written for an undergraduate-level course entitled, "Fantasy Football: Predictive Analytics and Empiricism".
The chapters provide an overview of topics—each of which could have its own class and textbook, such as [causal inference](causal-inference.qmd), [factor analysis](factor-analysis.qmd), [cluster analysis](cluster-analysis.qmd), [principal component analysis](pca.qmd), [machine learning](machine-learning.qmd), [cognitive biases](cognitive-bias.qmd), [modern portfolio theory](modern-portfolio-theory.qmd), [data visualization](data-visualization.qmd), [simulation](simulation.qmd), etc.
The book gives readers an overview of the breadth of the approaches to prediction and empiricism.
As a consequence, the book does not cover any one technique or approach in great depth.

@@

Skills in statistics, statistical programming, and data analysis are highly valuable.
This book includes practical and conceptual tools that build a foundation for critical thinking.
The book aims to help readers evaluate theory in the light of evidence (and vice versa) and to refine decision making in the context of uncertainty.
Readers will learn about the ways that psychological science (and related disciplines) poses questions, formulates hypotheses, designs studies to test those questions, and interprets the findings, collectively with the aim of answering questions, improving decision making, and solving problems.

@@

Here is a video of Professor Benjamin Motz that describes the value of teaching statistics through the lens of fantasy football [@NFL2014]:
